The Controlled Choice Design and Paternalism in Pawnshop Borrowing

### 2024-05-21 PacDev.tex
ecta submission

%\usetheme{Singapore}
%\usefonttheme{serif} 
\input{preambleBeamer.tex}

@@

\date{June 2023}

@@

\begin{frame}{Motivation: Private paternalism}
\begin{itemize}
    \vfill \item Many institutions —firms, schools, financial contracts— restrict choice using built-in commitment mechanisms which help workers, students, borrowers overcome self-control problems
    \begin{itemize}
        \item Loans with fixed repayment schemes, homework due dates, etc.
    \end{itemize}
    \vfill \pause\item At the same time these firms hide these forcing mechanisms and don’t market their commitment features, potentially because demand for them is low.
    \vfill  \item  Laibson (2018) argues that clients that benefit from commitment may underestimate its value, and that in such cases private paternalism (i.e. allocating them to commitment) could be beneficial.
    \vfill  \pause\item  \textbf{We study the (a) benefits of imposing a structured repayment contract on financing cost, (b) whether there is demand for such structure, and (c) whether non-takers of such a commitment product would benefit from taking it.}
\end{itemize}

@@

@@

\begin{frame}{Context}
\begin{itemize}
    \vfill \item Pawn loans involve borrowers leaving valuable liquid assets as collateral in exchange for an immediate cash loan
    \vfill \pause \item The loan is overcollateralized (loan is 70\% of appraised value) and collateral is liquid.
    \begin{itemize}
        \item The lender approves loans in a few minutes without income or credit history check $\rightarrow$ used for emergencies.
    \end{itemize}
  \vfill \pause \item Because the loan is overcollateralized and collateral is liquid, the lender may gain if the borrower defaults on the loan, especially if the borrower pays towards recovery on the way to default.
    \vfill \pause  \item Among those that lose their pawn (60\%), 48\% paid a positive amount towards its recovery and on average paid 42\% of loan.
    \vfill      \item This happens in spite (or because?) of 74\% of borrowers reporting a 100\% subjective probability recovery ex-ante. 
    %\vfill   \item 13\% of borrowers are classified as present biased using the simple standard question.
     \vfill \pause    \item In such an environment, one may ask if putting more structure/committment in payments may help borrowers recover their pawn.
     \vfill \pause    \item Not only that: Will the structure/commitment be demanded by all (or most) people who benefit?

@@

\section{Outline}
\begin{frame}{Outline}
     \begin{itemize}
         \vfill\item \textbf{Experimental Design}
         \vfill\item Main results
          \vfill\item Exploiting the Controlled Choice Design
         \vfill\item Paternalism
     \end{itemize}
\end{frame}

\section{Design}

\begin{frame}{Pawn contract}
    \begin{figure}[H]
    \label{ExplanatoryMaterial1}
    \begin{center}
        \includegraphics[width=0.45\textwidth]{Figuras/sq_contract.png}
    \end{center}
\end{figure}
\end{frame}

\begin{frame}{Structured payments contract}
   \begin{itemize}
       \vfill \item We designed a new contract that is identical to the status quo contract except that it enhances the regularity and salience of payments as a way to encourage repayment.
         \begin{figure}[H]
    \label{ExplanatoryMaterial2}
    \begin{center}
        \includegraphics[width=0.40\textwidth]{Figuras/fc_contract.png}
    \end{center}
\end{figure}

   \end{itemize}

% \begin{frame}{Structured payments contract}
%   \begin{itemize}

%       \vfill\item The purpose of the small fee was to mainly to make the structured schedule salient, not to be a large disincentive to be late. 
%       \begin{itemize}
%           \item Transportation cost to go to the branch to pay is on the same order of magnitude as the fee in average.
%       \end{itemize}
%       \vfill\item  The empirical literature provides some guidance that such a contract may decrease default and elicit demand.
%       \begin{itemize}
%           \item Field \& Pande (2008) find null effects of payment frequency on loan default for group lending (but samples are small and there is almost no default in the control).

%         \item  Bauer et al. (2012) estimate a positive correlation between measured present bias and selecting into microfinance, which they interpret as demand for structured payments.
%       \end{itemize}

%   \end{itemize}

% \end{frame}

@@

   \begin{equation*}
    \text{Financial Cost}_i =  \underbrace{\sum_t P^i_{it}}_{\text{Pay to Interest}} + \underbrace{\sum_t P^f_{it}}_{\text{Pay to Fees}}  + \mathds{1}(\text{Default}_i) \times \left[\text{(Appr. value - Loan Diff)}_i + \underbrace{\sum_t P^c_{it}}_{\text{Pay to Capital}} \right]
   \end{equation*}

@@

 \begin{frame}{Description}
 \label{consort}
 \begin{figure}[H]
      \caption{Experiment description}
     \label{exp_description}
 \begin{center}
         \includegraphics[width=0.80\textwidth]{Figuras/consort.pdf}
   \end{center}
 \end{figure}
 %\hyperlink{experimental_integrity}{\beamerbutton{Details}}

@@

\begin{frame}{Balance and Summary statistics}
    \begin{table}[H]
%\caption{Summary statistics and Balance}
\label{SS}
\begin{center}
\resizebox{.65\textwidth}{!}{
\scriptsize{\input{./Tables/SS.tex}}
}
\end{center}
%\textit{Do file: } \texttt{ss\_att.do}
\end{table}
% \hyperlink{data}{\beamerbutton{Back}}
\end{frame}

\begin{frame}{Outline}
     \begin{itemize}
         \vfill\item Experimental Design
         \vfill\item \textbf{Main results}
          \vfill\item Exploiting the Controlled Choice Design
         \vfill\item Paternalism 
     \end{itemize}
\end{frame}

\begin{frame}
\textbf{Predictors of take-up : $\Pr(Take up)=11\%$} on average.

\begin{figure}[H]
    \begin{center}
        \includegraphics[width=0.9\textwidth]{Figuras/determinants_choose_commitment.pdf}
    \end{center}
    \end{figure}
\end{frame}

@@

\begin{itemize}
    \item Financial cost reduced by \$379 pesos (20\% of mean). That is: charging fee + structure \textit{decreased} cost.
    \item Default decreases by 6.5pp (15\% of mean).
    \item APR decreases by 34 points, from mean of 184.
\end{itemize}
\vspace{.3in}
\begin{table}[H]
\begin{center}
\resizebox{0.95\textwidth}{!}{
\small{\input{./Tables/decomposition_main_te.tex}}
}
\end{center}
\end{table}

@@

\begin{table}[H]
\caption{Intermediate outcomes}
\begin{center}
\scriptsize{\input{./Tables/mechanism_pres1.tex}}
\end{center}
\end{table}
\vfill
%\hyperlink{intermediate_outcomes}{\beamerbutton{Back}}
 \begin{itemize}
     \item \textbf{Speed of payment:} The first payment of the forced commitment contract  occurs 13 days earlier, increasing the fraction who recover on the first visit by 7.9 pp. Conditional on recovering, they recover 28 days faster.
\end{itemize}
\end{frame}

@@

\begin{frame}{Intermediate outcomes (3)}

    \begin{table}[H]
\caption{Intermediate outcomes}
\begin{center}
\footnotesize{\input{./Tables/mechanism_pres3.tex}}
\end{center}
\end{table}
\vfill
%\hyperlink{intermediate_outcomes}{\beamerbutton{Back}}
 \begin{itemize}
     \item \vfill \textbf{Frequency of visits:} Commitment induces a `parting of the waters' whereby those who were going to default visit the branch subsequently .2 fewer times.
\end{itemize}
\end{frame}

@@

\section{Paternalism}
\begin{frame}{Choice and Heterogeneous Treatment Effects}
\label{choice_hte}
    \begin{itemize}
    \vfill \item  So, forcing commitment decreases APR dramatically.

    \vfill \item \textbf{Low demand:} In spite of this, given the opportunity, only 11\% of borrowers chose commitment.   
    \begin{itemize}
       \pause \item If the effect of commitment were homogeneous, this would be enough to conclude that the 89\% who did not choose it would have been financially better off if they had.
       \item However, we test and reject the null hypothesis of homogeneous treatment effects (Chernozhukov et. al. 2018).
    \end{itemize}

    \vfill \item The borrowers who did not choose commitment could simply be those who don’t need it?
    \pause \vfill \item The distribution of TE (i.e. $Y_{1i}-Y_{0i}$) is not identified, as one person is only observed in one treatment. However, it can be bounded using the two marginal dist $F_1$ and $F_0$.

\begin{frame}

\begin{figure}[H]
    \caption{Fan \& Park bounds for benefit in APR\% }
    \label{fig:FanPark}
    \begin{center}
        \caption{APR}
        \centering
        \includegraphics[width=0.7\textwidth]{Figuras/fan_park_bounds_apr.pdf}
    \end{center}

%\textit{Do file: } \texttt{fan\_park\_bnds.do}       
\end{figure}

\begin{itemize}
        \vfill \item \textbf{Many with benefits did not demand:} Making no parametric assumptions, we find that at least 30\% of individual borrowers benefit from commitment $\implies$ many did not demand even though TE is positive for them.

\end{itemize}

\begin{frame}{Outline}
     \begin{itemize}
         \vfill\item Experimental Design
         \vfill\item Main results
          \vfill\item \textbf{Exploiting the Controlled Choice Design}
         \vfill\item Paternalism 
     \end{itemize}
\end{frame}

\begin{frame}{Identification afforded by experiment}

Our 3-armed experiment + dual exclusion restriction allows us to estimate: 
\begin {itemize}
 \item Treatment Effect on the Treated (ToT), as with standard IV on one-sided non-compliance.
 \item Treatment on the Untreated (TUT), symmetric instrumentation for \textit{not} complying as compared to forcing arm.
\end{itemize}
\vspace{.2in}
Notation: 
\begin{itemize}
    \item Potential outcomes $(Y_0,Y_1,C)$
    \item Assignment: $Z \in \{0,1,2\}$, i.e. \{SQ,Com,Choice\}.  
    \item Treatment: $D \in \{0,1\} $, i.e. \{SQ,Com\}.
\end{itemize}

@@

\begin{itemize}
    \item $Z \independent (Y_0,Y_1,C)$, achieved by randomization
    \item $D = \mathbbm{1}(Z_i \neq 2) Z + \mathbbm{1}(Z_i=2) C$, i.e. \alert{being assigned to a contract has same effect as choosing it} (e.g. used in compulsory school attendance and returns to schooling lit).
\end{itemize}
\end{frame}

\begin{frame}{The Double Exclusion Restriction:}

With both of these exclusion restrictions in place:
\begin{itemize}
    \item Effect of (Control = Not Choosing) for non-choosers
    \item Effect of (Forcing = Choosing) for choosers.
    \end{itemize}
\begin{itemize}
    \item  $Y_i = \mathbbm{1}(Z_i =0) Y_{i0} + \mathbbm{1}(Z_i = 1)  Y_{i1}  + \mathbbm{1}(Z_i = 2) \left[(1 - C_i) Y_{i0} + C_i Y_{i1} \right].$
\end{itemize}

Prop:
\begin{itemize}
    \item ToT := $\mathbbm{E}(Y_{i1} - Y_{i0} | C_i = 1)$ is point-identified, and equals $\frac{\mathbbm{E}(Y_i|Z_i=2) - \mathbbm{E}(Y_i|Z_i =0)}{\mathbbm{E}(D_i|Z_i=2)} $
     \item TuT := $\mathbbm{E}(Y_{i1} - Y_{i0} | C_i = 0)$ is point-identified, and equals $\frac{\mathbbm{E}(Y_i|Z_i=1) - \mathbbm{E}(Y_i|Z_i =2)}{1-\mathbbm{E}(D_i|Z_i=2)} $
     \item Also identified: 
     \begin{itemize}
         \item Average Selection on Gains $ASG:=ToT-TuT$
         \item Average Seletion Bias $ASB:= \E[Y_0 | C=1]-\E[Y_0 | C=0]$
         \item Average Selection on Levels $ASL:= \E[Y_1 | C=1]-\E[Y_1 | C=0]$
     \end{itemize}
\end{itemize}
\end{frame}

@@

\begin{frame}{On avg. those that do not choose would benefit: TuT $>$ 0}
\begin{itemize}
    \vfill \item Commitment increases average financial benefit even for the subset of borrowers who \alert{don't choose to commit voluntarily}.
    \vfill \item Coefficient ToT>TuT, but cannot reject equality due to large s.e. in ToT.
    \vfill \item Results hold when imputing transport cost and lost wages per visit, and charge interest in amount paid (as a proxy for liquidity lost).
\end{itemize}
\vspace{.2in}
\begin{table}[H]
%those who are most likely to benefit from it and those whose outcomes are most adverse under the status quo.
\label{tot_tut}
\begin{center}
\small{\input{./Tables/tot_tut.tex}}
\end{center}
\end{table}
\end{frame}

@@

\section{Outline}
\begin{frame}{Outline}
     \begin{itemize}
         \vfill\item Experimental Design
         \vfill\item Main results
          \vfill\item Exploiting the Controlled Choice Design
         \vfill\item \textbf{Paternalism}
     \end{itemize}
\end{frame}

\begin{frame}{If commitment works, why don't people choose it?}
    \begin{itemize}
         \onslide<1>{\item Need to learn about it}
         \onslide<2>{\item Discounting}
        \onslide<3-4>{\item Present-Bias}
    \end{itemize}

@@

\only<4>{

    \begin{itemize}
    \item   We estimate the TuT conditional on $X_i=1$ or $X_i=1$ (say $X_i= PB_i$ or $=Confidence_i$) and see which sub-populations have larger TuT.

\vspace{.3in}
    \begin{align*}
        1=& \frac{\mathbb{E}[Y_{1i}-Y_{0i} | C_i=0, X_i=1]}{TuT}\Pr(X_i=1 | C_i=0) \\
        \quad &+ \frac{\mathbb{E}[Y_{1i}-Y_{0i}| C_i=0, X_i=0]}{TuT}\Pr(X_i=0 | C_i=0)
    \end{align*}

%and we will say that the variable $B_i$ explains the ToT whenever one of the terms (ratio weighted by the probability) is statistically significant from zero, (close to one), and the other term is statistically zero.
    \end{itemize}
}

@@

\begin{frame}{Determinants of Sure Confidence}

        \begin{figure}
        \caption{What attributes correlate with Sure Confidence?}
        \centering
        \includegraphics[width=0.65\textwidth]{Figuras/determinants_confidence_100.pdf}
        \end{figure}

The Sure-Confident are:
\begin{itemize}
    \item   Older, more educated men who
    \item   Have savings and do not report financial stress or trouble meeting bills, and 
    \item   Are likely to be relied upon by family members.
\end{itemize}

@@

\item We use (Athey et.al. 2019) GRF to estimate CATE (causal RF), CTUT and CTOT (instrumental RF).

\begin{itemize}	
	\item We split the data that produce the biggest difference in TE across leaves, by still producing accurate estimates of the TE. Moreover, the splits are made honest by taking the training data and splitting it into two subsamples: a splitting subsample and an estimating subsample. \hyperlink{honest_causal_tree}{\beamerbutton{Honest Causal Tree}}   
\end{itemize}

\item Estimated TE in each leaf is aysmptotically normal. 
\end{itemize}

    \begin{figure}
        \caption{CATT (APR)}
        \centering
        \includegraphics[width=0.5\textwidth]{Figuras/he_dist_tau_hat_tut.pdf}
        \end{figure}

 \begin{itemize}
\item We test and reject the null hypothesis of homogeneous treatment effects (Chernozhukov et. al. 2018)
 \end{itemize}       
\end{frame}

\begin{frame}{Example of a Causal Tree}

    \begin{figure}
        \caption{Causal Tree}
        \centering
\includegraphics[width=0.8\textwidth]{Figuras/crf_apr.pdf}
        \end{figure}

\begin{frame}{Fraction that forgo benefit:  Choice Arm}

@@

\begin{frame}{Fraction that forgo benefit:  Forcing Arm}

        \begin{figure}
         \label{better_forceall}
        \caption{Effect of forcing everyone}
        \centering
        \includegraphics[width=0.65\textwidth]{Figuras/cdf_CATE.pdf}
        \end{figure}

\begin{itemize}
    \item   Now use Random Forest to estimate the CATE of forcing, examine heterogeneity in ATE.
    \item   Because CATE>CTUT, we now find fully 91\% of individuals better off being forced into commitment than staying in control.
\end{itemize}

@@

\begin{frame}{Comparing `Wide' and `Narrow' Heterogeneity}

    \label{wide_v_narrow}

        \begin{figure}
        \caption{Scatterplot of Predicted Heterogeneity}
        \centering
        \includegraphics[width=0.75\textwidth]{Figuras/scatter_hist_wide_narrow.pdf}
        \end{figure}

\begin{itemize}
    \item   Substantially less heterogeneity fitting APR CATE with `narrow' than `wide'
    \item Test of homogeneity (Chernozhukov et. al. 2018) no longer rejected with `narrow'
    \item   However, overall fitted relationship shows `narrow' adjusts to the mean TE.
\end{itemize}

\begin{frame}{Comparison of Targeting Performance:  CDFs}

        \begin{figure}
        \label{targeting_CDFs}
        \caption{Distribution of Benefits under Different Targeting Rules}
        \centering
        \includegraphics[width=0.70\textwidth]{Figuras/wide_narrow_rule.pdf}
        \end{figure}

\begin{itemize}
    \item   Even using the Random Forest to target, our four `narrow' variables only increase the fraction benefitting from 91\% (all Forced) to ~93\% (targeted).
    \item  Using a Logit with the `narrow' variables actually worsens performance relative to universal Forcing because Logit matches benefit/loss fraction, has both Type 1 and Type 2 errors.
\end{itemize}

@@

\section{Conclusion}
\begin{frame}{Conclusion}
    \begin{itemize}
     \vfill \item Laibson has spoken of `veiled paternalism' in contexts where principals desire reliability; here we have a case of `veiled non-paternalism' where features encouraging default might be embedded.
     \vfill \item Novel design to study essential heterogeneity: ``Controlled Choice''
        %\begin{itemize}
         %   \item Combine ``Controlled Choice'' with MTE: Can we extend results of Mogstad et al (2017) to use our ATE, TUT, and TOT as additional inequality restrictions that constrain partial identification bounds for MTEs?
        %\end{itemize}
        \vfill \item  APR reduced by 34\% in the commitment arm
        \vfill  \item Results suggest selection on gains, but still large effects of imposing commitment on non-takers.
        \vfill \item Mystery of low take-up combined with large TuT seems best explained by sure-confidence among pawnshop customers.
        \vfill\item  Ability to target paternalism using objective covariates is poor; even using RF without cross-validation gains from targeting are small and with logit actually makes things worse.
        \vfill \item Suggests mandated commitment-based contract structures in payday/pawnshop loans as a form of pro-poor regulation?
    \end{itemize}  
\end{frame}

>>>>

%\usetheme{Singapore}
%\usefonttheme{serif} 
\input{preambleBeamer.tex}
\usepackage{comment}

@@

\date{PACDEV, March 2023}

@@

\begin{frame}{Motivation: Private paternalism}
\begin{itemize}
    \item Many institutions —firms, schools, financial contracts— restrict choice using built-in commitment mechanisms which help workers, students, borrowers overcome self-control problems
    \begin{itemize}
        \item Loans with fixed repayment schemes, homework due dates, etc.
    \end{itemize}
    \item At the same time these firms hide these forcing mechanisms and don’t market their commitment features, potentially because demand for them is low.
     \item  Laibson (2018) argues that clients that benefit from commitment may underestimate its value, and that in such cases private paternalism (i.e. allocating them to commitment) could be beneficial.
    \item  \textbf{We study the (a) benefits of imposing a structured repayment contract on financing cost, (b) whether there is demand for such structure, and (c) whether non-takers of such a commitment product would benefit from taking it.}
\end{itemize}

@@

\begin{frame}{Context}
\begin{itemize}
     \item Pawn loans involve borrowers leaving valuable liquid assets as collateral in exchange for an immediate cash loan
     \item The loan is overcollateralized (loan is 70\% of appraised value) and collateral is liquid.
    \begin{itemize}
        \item The lender approves loans in a few minutes without income or credit history check $\rightarrow$ used for emergencies.
    \end{itemize}
  \item Because the loan is overcollateralized and collateral is liquid, the lender may gain if the borrower defaults on the loan, especially if the borrower pays towards recovery on the way to default.
     \item Among those that lose their pawn (44\%), 48\% paid a positive amount towards its recovery and on average paid 42\% of loan.
     \item This happens in spite (or because?) of 74\% of borrowers reporting a 100\% subjective probability recovery ex-ante. 
    %\vfill   \item 13\% of borrowers are classified as present biased using the simple standard question.
        \item In such an environment, one may ask if putting more structure/committment in payments may help borrowers recover their pawn.
      \item Not only that: Will the structure/commitment be demanded by all (or most) people who benefit?

@@

@@

@@

\begin{align*}
    \text{Financial Cost}_i =&  \sum_t P^I_{it} +\sum_t P^F_{it}  
     + \mathds{1}(\text{Default}_i) \times \left(\text{Value}_i-\text{Loan}_i + \sum_t P^c_{it}\right)
\end{align*}

@@

@@

@@

\begin{itemize}
    \item  Takeup of commitment in Choice arm is only 11\%.
    \item Financial cost reduced by \$204 pesos (20\% of mean). That is: charging fee + structure \textit{decreased} cost.
    \item Default decreases by 6.5pp (15\% of mean), APR decreases by 11 points, from mean of 57\%.
\end{itemize}
\vspace{.3in}
\begin{table}[H]
\begin{center}
\resizebox{0.95\textwidth}{!}{
\small{\input{./Tables/decomposition_main_te.tex}}
}
\end{center}
\end{table}

@@

\begin{table}[H]
\caption{Intermediate outcomes}
\begin{center}
\scriptsize{\input{./Tables/mechanism_pres1.tex}}
\end{center}
\end{table}
\vfill
%\hyperlink{intermediate_outcomes}{\beamerbutton{Back}}
 \begin{itemize}
     \item \textbf{Speed of payment:} The first payment of the forced commitment contract  occurs 14 days earlier, increasing the fraction who recover on the first visit by 7.9 pp. Conditional on recovering, they recover 28 days faster.
\end{itemize}
\end{frame}

@@

@@

\begin{frame}{Using a Double Exclusion Restriction}

Our 3-armed experiment + dual exclusion restriction allows us to estimate: 
\begin {itemize}
 \item Treatment Effect on the Treated (ToT), as with standard IV on one-sided non-compliance.
 \item Treatment on the Untreated (TUT), symmetric instrumentation for \textit{not} complying as compared to forcing arm.
\end{itemize}
\vspace{.2in}

\begin{itemize}
    \item $Z \independent (Y_0,Y_1,C)$, achieved by randomization
    \item $D = \mathbbm{1}(Z_i \neq 2) Z + \mathbbm{1}(Z_i=2) C$, i.e. \alert{being assigned to a contract has same effect as choosing it} (e.g. used in compulsory school attendance and returns to schooling lit).
\end{itemize}

@@

Prop:
\begin{itemize}
    \item ToT := $\mathbbm{E}(Y_{i1} - Y_{i0} | C_i = 1)$ is point-identified, and equals $\frac{\mathbbm{E}(Y_i|Z_i=2) - \mathbbm{E}(Y_i|Z_i =0)}{\mathbbm{E}(D_i|Z_i=2)} $
     \item TuT := $\mathbbm{E}(Y_{i1} - Y_{i0} | C_i = 0)$ is point-identified, and equals $\frac{\mathbbm{E}(Y_i|Z_i=1) - \mathbbm{E}(Y_i|Z_i =2)}{1-\mathbbm{E}(D_i|Z_i=2)} $
     \item Also identified: 
     \begin{itemize}
         \item Average Selection on Gains $ASG:=ToT-TuT$
         \item Average Selection Bias $ASB:= \E[Y_0 | C=1]-\E[Y_0 | C=0]$
         \item Average Selection on Levels $ASL:= \E[Y_1 | C=1]-\E[Y_1 | C=0]$
     \end{itemize}
\end{itemize}
\end{frame}

@@

\begin{frame}{On avg. those that do not choose would benefit: TuT $>$ 0}
\begin{itemize}
    \vfill \item Commitment increases financial benefit even for borrowers who don't choose  it.
    \vfill \item APR, FC ToT>TuT, but cannot reject equality due to large s.e. in ToT.
\end{itemize}
\vspace{.2in}
\begin{table}[H]
%those who are most likely to benefit from it and those whose outcomes are most adverse under the status quo.
\label{tot_tut}
\begin{center}
\small{\input{./Tables/tot_tut.tex}}
\end{center}
\end{table}
\end{frame}

@@

\begin{frame}{If commitment works, why don't people choose it?}
    \begin{itemize}
         \onslide<1>{\item Need to learn about it}
         \onslide<2>{\item Discounting}
        \onslide<3>{\item Present-Bias}
    \end{itemize}

@@

@@

@@

\item We use (Athey et.al. 2019) GRF to estimate CATE (causal RF), CTUT and CTOT (instrumental RF).
\end{itemize}

@@

@@

@@

\section{Conclusion}
\begin{frame}{Conclusion}
    \begin{itemize}
     \vfill \item Laibson has spoken of `veiled paternalism' in contexts where principals desire reliability; here we have a case of `veiled non-paternalism' where features encouraging default might be embedded.
     \vfill \item Novel design to study essential heterogeneity: ``Controlled Choice''
        %\begin{itemize}
         %   \item Combine ``Controlled Choice'' with MTE: Can we extend results of Mogstad et al (2017) to use our ATE, TUT, and TOT as additional inequality restrictions that constrain partial identification bounds for MTEs?
        %\end{itemize}
        \vfill \item  APR reduced by 19\% in the commitment arm
        \vfill \item Mystery of low take-up combined with large TuT seems best explained by sure-confidence among pawnshop customers.
        \vfill\item  Ability to target paternalism using objective covariates is poor; even using RF without cross-validation gains from targeting are small and with logit actually makes things worse.
        \vfill \item Suggests mandated commitment-based contract structures in payday/pawnshop loans as a form of pro-poor regulation?
    \end{itemize}  
\end{frame}

### 2024-05-21 donde.tex
ecta submission

We apply this approach to an important and understudied context: pawnshop lending. 
Pawn loans constitute one of the oldest and most prevalent forms of borrowing \citep{carter2012pawnshops}.
Our partner lender, for example, made over 4 million loans to more than a million clients during the past three years.\footnote{For comparison, there were 2.3 million microfinance clients in Mexico in 2009 \citep{Pedroza:2010}.} 
The question of choice versus paternalism is particularly salient in this context, as choice mistakes could arise from borrowers' low education and the fact that they typically borrow for emergencies under significant stress.\footnote{A large literature shows  stress impairs cognitive function, e.g. \cite{StressReview}.}
%\footnote{There are more than 11,000 pawn shops across the US, with 30 million clients and \$14 billion yearly revenues (in China it is a \$43 billion industry).  \url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}.}
Our experiment covers just under 5,000 pawnshop clients in 6 of our partner lender's Mexico City branches. Our control arm illustrates the costs of the status quo contract: fully \emph{44\%} of borrowers default, losing lose their pawn along with any payments made towards principal.\footnote{High pawn default rates are common, in the US they oscilate around 15\% (see \href{https://tinyurl.com/yc2x5bjf}{here}).} Our ``commitment choice'' arm gives borrowers the chance to opt into a structured repayment contract when taking a loan. The structured contract requires borrowers to make three monthly payments rather than one balloon payment at the end, with each monthly payment including the accrued interest at that time as well as a nominal fee of 2\% of that month's payment if the payment is delinquent. The fee serves as a reminder and a means of reinforcing the importance of these interim payments. In our ``forced commitment'' arm all borrowers are \emph{required} to repay using the same structured monthly contract offered on an opt-in basis in the commitment choice arm.

>>>>

We apply this approach to an important and understudied context: pawnshop lending. 
Pawn loans constitute one of the oldest and most prevalent forms of borrowing \citep{carter2012pawnshops}.
Our partner lender, for example, made over 4 million loans to more than a million clients during the past three years.\footnote{For comparison, there were 2.3 million microfinance clients in Mexico in 2009 \citep{Pedroza:2010}.} 
The question of choice versus paternalism is particularly salient in this context, as choice mistakes could arise from borrowers' low education and the fact that they typically borrow for emergencies under significant stress.\footnote{A large literature shows  stress impairs cognitive function, e.g. \cite{StressReview}.}
%\footnote{There are more than 11,000 pawn shops across the US, with 30 million clients and \$14 billion yearly revenues (in China it is a \$43 billion industry).  \url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}.}
Our experiment covers just under 5,000 pawnshop clients in 6 of our partner lender's Mexico City branches. Our control arm illustrates the costs of the status quo contract: fully \emph{44\%} of borrowers default, losing lose their pawn along with any payments made towards principal.\footnote{High pawn default rates are common, in the US they oscillate around 15\% (see \href{https://tinyurl.com/yc2x5bjf}{here}).} Our ``commitment choice'' arm gives borrowers the chance to opt into a structured repayment contract when taking a loan. The structured contract requires borrowers to make three monthly payments rather than one balloon payment at the end, with each monthly payment including the accrued interest at that time as well as a nominal fee of 2\% of that month's payment if the payment is delinquent. The fee serves as a reminder and a means of reinforcing the importance of these interim payments. In our ``forced commitment'' arm all borrowers are \emph{required} to repay using the same structured monthly contract offered on an opt-in basis in the commitment choice arm.
